
\section{Specific Requirements}\label{sec:spec_req}

Here we include more details on all aspects in Section 2 if they
can be useful for the development team. 

\subsection{External Interface Requirements}
\subsubsection{User Interfaces}
\subsubsection{Hardware Interfaces}
\subsubsection{Software Interfaces}
\subsubsection{Communication Interfaces}
\subsection{Functional Requirements}
Definition of use case diagrams, use cases and associated
sequence/activity diagrams, and mapping on requirements

\begin{enumerate}[label={[R\arabic*]}]
    % Users
    \item Allow a User to find Stores nearby a specified location.
    \item Allow a User to get in the virtual line.
    \item Allow a User to preview an estimate of the queue time.
    \item Allow a User to cancel their reservation.
    \item Allow a User to retrieve a scannable QR Code/Barcode that they must present in order to be granted access to a store.
    \item Allow a User to sign up for an Account after providing a mobile phone number.
    \item Allow a registered User to book a visit for themselves or for someone else to a specific store.

    % Store
    \item The System notifies the Users affected by delay.
    \item The System postpones Users visits in case of a delay.
    \item The System enforces the limits on the allowed number of concurrent Customers inside a store.
    \item The System does not admit Users that arrive earlier, even if the current number of Customers isn't maximum.
    \item The System grants a User access only after the User's time of reservation.
    \item The System invalidates a User's reservation if they do not show up during a certain time interval.
    \item The System reserves a certain number of the allowed quote of customers for a special category of Users.
    \item The system grants priority access to Users without a reservation that show up at the store and are pregnant women, elderly or with disabilities.
    
    % System Managers
    \item Allow System Managers to set a limit to the people allowed into the store at a time.
    \item Allow System Managers to not provide the physical ticket option.
    \item Allow System Managers to enable the functionality that allows customers to link their Account with Loyalty Program feature.
\end{enumerate}

\begin{center}
    \begin{tabular}{ |c||c|c| }
        \hline
        \textbf{Goal} & \textbf{Requirements} & \textbf{Assumptions} \\
        \hline
        G1 & R1, R2, R3, R4, R5, R6 & \\
        \hline
        G2 & R3, R7, R8, & \\
        \hline
        G3 & R5, R10 & \\
        \hline
        G4 & & \\
        \hline
        G5 & & \\
        \hline
    \end{tabular}
\end{center}

\subsection{Performance Requirements}
\subsection{Design Constraints}
\subsubsection{Standards Compliance}
\subsubsection{Hardware Limitations}
\subsubsection{Any Other Constraint}
\subsection{Software System Attributes}
\subsubsection{Reliability}
\subsubsection{Availability}
\subsubsection{Security}
\subsubsection{Maintainability}
\subsubsection{Portability}