\documentclass[a4paper]{article}

% imoprts

\usepackage{xargs}
\usepackage[pdftex,dvipsnames]{xcolor}
\usepackage[colorinlistoftodos,prependcaption,linecolor=yellow!30,backgroundcolor=yellow!30,bordercolor=yellow!30]{todonotes}

% commands definition

\newcommandx{\warning}[2][1=]{\todo[linecolor=red!30,backgroundcolor=red!30,bordercolor=red!30,#1]{#2}}
\newcommandx{\request}[2][1=]{\todo[linecolor=blue!30,backgroundcolor=blue!30,bordercolor=blue!30,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=green!30,backgroundcolor=green!30,bordercolor=green!30,#1]{#2}}

%------------------------------------------------------------------------------------

\begin{document}

\listoftodos

\tableofcontents

\section{Introduction}
General introduction. \todo{This is a todo}Text.

General introduction. \warning{This is a warning}Text.

General introduction. \request{This is a request}Text.

General introduction. \info{This is an info}Text.
\subsection{Purpose}
This document is the Requirement Analysis and Specification Document for the Customers Line-Up system.
The purpose of this document is to describe the system focusing on scenarios, use cases, requirements and specifications,
analyzing what the software will do, how it will be used and the constraints under which it will operate.
This document is intended both for users and developers.

\subsection{Scope}
Customers Line-Up is a tool that allows managers to regulate the influx of people in physical stores and offers
people a number of functionalities aimed at reducing the time spent waiting in line.
The objective of the system is to help businesses abide by the regulation imposing limits on the number of people
who can visit stores at a time and prohibit the formation of crowds such as long lines.
This objective will be reached offering a number of functionalities, including:\todo{revise/add more}
\begin{itemize}
    \item monitoring the number of people in a store
    \item booking a visit, notifying any change in the schedule when it is needed
    \item suggest alternate stores and/or time frames
    \item tracking the actions of the customer and predicting their future behavior
\end{itemize}

\subsection{Definitions, Acronyms, Abbreviations}
\subsection{Revision History}
\subsection{Reference History}
\subsection{Document Structure}
\section{Overall Description}
\subsection{Product Perspective}
\subsection{Product Functions}
\subsection{User Characteristics}
\subsection{Assumptions, Dependencies, and Constraints}
\section{Specific Requirements}
\subsection{External Interface Requirements}
\subsubsection{User Interfaces}
\subsubsection{Hardware Interfaces}
\subsubsection{Software Interfaces}
\subsubsection{Communication Interfaces}
\subsection{Functional Requirements}
\subsection{Performance Requirements}
\subsection{Design Constraints}
\subsubsection{Standards Compliance}
\subsubsection{Hardware Limitations}
\subsubsection{Any Other Constraint}
\subsection{Software System Attributes}
\subsubsection{Reliability}
\subsubsection{Availability}
\subsubsection{Security}
\subsubsection{Maintainability}
\subsubsection{Portability}
\end{document}
